Experiment 3: ratings

### 2021-06-04 analysis/exp3_analysis.Rmd
added child comparison graphs

child_agg <- child_long %>% group_by(drop, target, relation) %>%
  summarize(chose_target = mean(chose_target))

@@

## Compare adult choice proportions vs. likelihood proportions

@@

>>>>

child_agg <- child_long %>% group_by(drop, target, relation) %>%
  summarize(chose_target = mean(chose_target, na.rm=T))

@@

## Compare adult choices to ratings-derived proportions

@@

## Compare children's choices to ratings-derived proportions

```{r}
p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")
